Modelling the emergence of whisker barrels

### 2020-07-01 paper/briefpaper/brief.tex
Fig 5 caption

\begin{center}
  \includegraphics[width=\linewidth]{./Fig5.png}
  \captionof{figure}{\MPthreePred{Simulating whisker trimming by reduction of
      $\epsilon$ for the thalamocortical projection for barrel C3, for which
      $i=13$. All other model parameters match those in
      Fig.\,\ref{fig:main}C. \textbf{A} Graph of individual barrel measures
      plotted vs.~the multiplier applied to $\epsilon_{13}$. \textbf{B} The
      pattern for $\epsilon_{m}=0.64$.}}
  \label{fig:whiskertrim}
\end{center}

>>>>

\begin{center}
  \includegraphics[width=\linewidth]{./Fig5.png}
  \captionof{figure}{\MPthreePred{Simulating whisker trimming by reduction of
      $\epsilon_i$ for the thalamocortical projection for barrel
      C3. $\epsilon_{C3} = m \epsilon$, where otherwise, all model parameters
      match those in Fig.\,\ref{fig:main}C (thus $\epsilon=1.2$). \textbf{A}
      The pattern formed after 30000 steps for $m=0.64$. Barrel C3 is reduced
      in size as its axon branching competes less strongly with its
      neighbours, whose area is slightly increased. \textbf{B} Top: Individual
      barrel area, $A_i$, plotted vs.~$m$ shows that as $m$ is reduced, the
      area of C3 (blue squares) goes down, disappearing for $m\approx0.5$,
      whereas the areas of neighbouring barrels (triangles) increases. Bottom:
      Honda measures of the Dirichliform nature of the pattern. Red circles
      show the overall Honda-$\delta$ measure, with the red dotted line
      showing the same `good' pattern threshold shown in
      Fig.\,\ref{fig:main}D. Blue squares and triangles show the
      \emph{individual} Honda metric ($\delta_i$ here; $\Delta_j$ in}
    \citealp{honda_geometrical_1983}) \MPthreePred{divided by the barrel area,
      making it comparable with the dimensionless, overall Honda-$\delta$
      metric. The individual Honda measures do not vary systematically with
      $m$.}}
  \label{fig:whiskertrim}
\end{center}
